Reading Notes

### 2020-09-03 1summ.tex
draft pass at im and bi sections

IM - Potential to advance knowledge and understanding within own and across different fields
- Activities explore creative, original, or potentially transformative concepts?
A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This can be useful for screening of potential OPV compounds.
what makes a good NFA?

- Plan well-reasoned, well organized, based on sound rationale?

- Mechanism to assess success?
%%<comparing mobilities, diffraction to experiment>

- How qualified is team?
%%<talk about what I've done already?>

- Adequate resources to carry out activities?
%%<talk about our supercomputer allocations?>

%\required{Broader Impacts}
\begin{center}
    \textbf{Broader Impacts}
\end{center}
% There are 4 kinds of broader impacts.
% 1. advance discovery and understanding while promoting teaching,
% training and learning
% 2. broaden the participation of underrepresented groups
% 3. disseminated broadly to enhance scientific and technological
% understanding
% 4. benefits of the proposed activity to society

@@

BI - Potential to benefit society, contribute to achievement of desired societal outcomes
- Activities explore creative, original, or potentially transformative concepts?
%%<talk about VOTCA?>
%%<talk about TRUE simulations and reproducibility in the field>

- Plan well-reasoned, well organized, based on sound rationale?

- Mechanism to assess success?
a sign of well-written, understandable code is if other people use it. 
It's tricky because this is completely out of my control, but if other people find my code useful--it is a success.
by integrating what I do with other existing codebases I can help to achieve this goal.
Also having good tutorials and documentation.

- How qualified is team?
Helping to make research transferrable, reproducible, useable, and extensible. 
Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
Training/teaching undergrads.
Working as part of a team.

- Adequate resources to carry out activities?
oss community
software carpentry training
experience with teaching/training undergrads

>>>>

This proposal has the potential to transform the manufacturing of sustainable low-cost power generation
A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This is an important step for screening potential OPV compounds.

This proposal has a the potential to transform the norms of molecular simulation.
By developing software with a focus on transferrability, reproducibility, usability, and extensibility and thinking beyond just solving a problem but thinking about how to solve the problem for the end-user we can help to change the norms in the computational sciences.
While we recognise the proposed work is challenging, we are positioned for success based on our prior work developing proofs of concept and molecular simulation on gpus.

\begin{center}
    \textbf{Broader Impacts}
\end{center}
% There are 4 kinds of broader impacts.
% 1. advance discovery and understanding while promoting teaching,
% training and learning
% 2. broaden the participation of underrepresented groups
% 3. disseminated broadly to enhance scientific and technological
% understanding
% 4. benefits of the proposed activity to society

@@

Bring new students in to the software development process.
Helping to make research transferrable, reproducible, useable, and extensible. 
Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
Training/teaching undergrads.
Working as part of a team.

All code-bases will be free and open source with tutorial and documentation so that not only are they available but accessible.
By integrating what I do with other existing codebases I can help to achieve this goal.
